---
title: "Asopinae of the World"
format: html
---

## Introduction

**Asopinae of the World** is the result of an effort to gather distribution data of Asopinae species around the World. These data are freely available for download. 

Using data from the literature and museum specimens, we recorded XXXX records for XXX species of Asopinae and made them available in XXXX et al XXXX. We hope to further expand the database, as more species and records are described. 

Here, you can check the species we compiled, and how many records for each one.
There is also a plot with how many species we compiled for each country. 

Across the website, you can also visualize a map with all records, check the raw data and download it, find the bibliography used to compile the data, and find the contacts of the collaborators. 




``` {r}
#| echo: false
#| output: false
 
library(tidyverse)
library(reactable)
library(leaflet)
library(htmlwidgets)
library(crosstalk)
library(bslib)
library(bsicons)
library(summarywidget)

```



``` {r}
#| echo: false
#| output: false
#| include: false

#READ DISTRBUTION DATA
asop <- read.csv("Asopinae_Analises_R_Preparado.csv", sep = ",")
asop <- asop %>%
  na.omit(asop) 
colnames(asop) <- c("Genus", "Species", "X_Longitude", "Y_Latitude", "Country", "Continent","Ecoregion", "Realm")

asop$X_Longitude <- as.numeric(asop$X_Longitude) 
asop$Y_Latitude <- as.numeric(asop$Y_Latitude)

row.names(asop) <- NULL

shared_asop <- SharedData$new(asop, group = "Asop")

share_species <- asop %>%
  select(Species) %>%
  unique() %>%
  SharedData$new(group = "Asop")
```




``` {r valueboxes}
#| echo: false
bscols(
  value_box(
    title = "Records",
    value = summarywidget(shared_asop),
    showcase = bsicons::bs_icon("search"),
    theme = value_box_theme(bg = "#756AB6", fg = "#F3EEEA"),
    width = 0.1
  ),
  
    value_box(
    title = "Species",
    value = summarywidget(share_species),
    showcase = bsicons::bs_icon("search"),
    theme = value_box_theme(bg = "#756AB6", fg = "#F3EEEA"),
    width = 0.1
  )
  
)

```

&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

## Species in the database


``` {r gráfico n de registros}
#| echo: false
#| warning: false

regs <- read.csv("continents_countries.csv") %>%
  select(Species, Count, Conts, Number_Cont, Cntrs, Number_Cntr)

shared_plot <- SharedData$new(regs)


filter_select("Species", "Species", shared_plot, ~Species)
  
reactable(
  shared_plot,
  defaultColDef = colDef(
      align = "center",
      headerStyle = list(background = "#f7f7f8")
    ),
  columns = list(
      Species = colDef(name = "Species"),
      Count = colDef(name = "Number of Records"),
      Conts = colDef(name = "Continents Occuring"),
      Number_Cont = colDef(name = "Number of Continents Occuring"),
      Cntrs = colDef(name = "Countries Occuring"),
      Number_Cntr = colDef(name = "Number of Countries Occuring")
    ),
  highlight = TRUE 
)




```


&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;


## Countries in the database

``` {r grafico paises}
#| echo: false
#| warning: false

share_countries <- asop %>%
  group_by(Country) %>%
  summarise(richness = length(unique(Species))) %>%
  data.table::as.data.table() %>%
  data.table::setkey(richness) %>%
  as.data.frame() %>%
  SharedData$new()


filter_select("Country", "Country", share_countries, ~Country)

library(plotly)

fig <- plot_ly(
    share_countries,
    x = ~Country, 
    y = ~richness,
    type = "bar"
)
fig
```


&nbsp;
&nbsp;
&nbsp;
&nbsp;




